Binning Strategies and Related Loss for Large Data

### 2015-02-27 Paper.Rnw
add Hadley "bin-summarize-smooth" paper and Liu "imMens" paper citations to bib

\ktm{ A number of scatterplot adaptations have been introduced that avoid overplotting by manipulating point locations or location scales.  Generalized scatterplots \citep{GeneralizedScatter} display all individual observations but use distortion of the point locations to avoid overlapping points. A extension of generalized scatterplots uses clustering and local principal components to allow ellipsoid oriented distortion to display local correlation structure in the data \citep{EllipseScatter}. Variable binned scatterplots \citep{hao2010visual} break the display into a non-uniform rectangular grid and resize the rows of cells according to density of points. This variable binning fragments the continuity of the axes into many segments on different scales. Theses approachs make fine data structure more visible and allows color to be reserved for a third variable instead of frequency; however, the distortion of the point locations or the axes wrap the visual display of the association between the two primary variables.}

One approach to reduce the graphical complexity is to bin the displayed data. This has the additional advantage of reducing the size of the stored data, as only the bin centers and the frequency of points which correspond to that bin must be stored.

>>>>

\ktm{ A number of scatterplot adaptations have been introduced that avoid overplotting by manipulating point locations or location scales.  Generalized scatterplots \citep{Keim2010GenScatter} display all individual observations but use distortion of the point locations to avoid overlapping points. A extension of generalized scatterplots uses clustering and local principal components to allow ellipsoid oriented distortion to display local correlation structure in the data \citep{Janetzko2013Ellipse}. Variable binned scatterplots \citep{Hao2010visual} break the display into a non-uniform rectangular grid and resize the rows of cells according to density of points. This variable binning fragments the continuity of the axes into many segments on different scales. Theses approachs make fine data structure more visible and allows color to be reserved for a third variable instead of frequency; however, the distortion of the point locations or the axes wrap the visual display of the association between the two primary variables.}

One approach to reduce the graphical complexity is to bin the displayed data. This has the additional advantage of reducing the size of the stored data, as only the bin centers and the frequency of points which correspond to that bin must be stored. \ktm{ Add \citep{Wickham2013Bin}  \citep{Liu2013imMens} here to argue the merits of binning. }
